### 2022-08-31 paper.tex
Started LaTeX paper

%
% File acl2020.tex
%
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

%\aclfinalcopy % Uncomment this line for the final submission
%\def\aclpaperid{***} %  Enter the acl Paper ID here

%\setlength\titlebox{5cm}
% You can expand the titlebox if you need extra space
% to show all the authors. Please do not make the titlebox
% smaller than 5cm (the original size); we will check this
% in the camera-ready version and ask you to change it back.

\newcommand\BibTeX{B\textsc{ib}\TeX}

\title{Instructions for ACL 2020 Proceedings}

\author{First Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
This document contains the instructions for preparing a manuscript for the proceedings of ACL 2020.
The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
These instructions should be used for both papers submitted for review and for final versions of accepted papers.
Authors are asked to conform to all the directions reported in this document.
\end{abstract}

\section{Credits}

This document has been adapted
by Steven Bethard, Ryan Cotterrell and Rui Yan
from the instructions for earlier ACL and NAACL proceedings, including those for 
ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
NAACL 2019 by Stephanie Lukin and Alla Roskovskaya, 
ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
NAACL 2018 by Margaret Michell and Stephanie Lukin,
2017/2018 (NA)ACL bibtex suggestions from Jason Eisner,
ACL 2017 by Dan Gildea and Min-Yen Kan, 
NAACL 2017 by Margaret Mitchell, 
ACL 2012 by Maggie Li and Michael White, 
ACL 2010 by Jing-Shing Chang and Philipp Koehn, 
ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
ACL 2002 by Eugene Charniak and Dekang Lin, 
and earlier ACL and EACL formats written by several people, including
John Chen, Henry S. Thompson and Donald Walker.
Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.

\section{Introduction}

The following instructions are directed to authors of papers submitted to ACL 2020 or accepted for publication in its proceedings.
All authors are required to adhere to these specifications.
Authors are required to provide a Portable Document Format (PDF) version of their papers.
\textbf{The proceedings are designed for printing on A4 paper.}

\section{Electronically-available resources}

ACL provides this description and accompanying style files at
\begin{quote}
\url{http://acl2020.org/downloads/acl2020-templates.zip}
\end{quote}
We strongly recommend the use of these style files, which have been appropriately tailored for the ACL 2020 proceedings.

\paragraph{\LaTeX-specific details:}
The templates include the \LaTeX2e{} source (\texttt{\small acl2020.tex}),
the \LaTeX2e{} style file used to format it (\texttt{\small acl2020.sty}),
an ACL bibliography style (\texttt{\small acl\_natbib.bst}),
an example bibliography (\texttt{\small acl2020.bib}),
and the bibliography for the ACL Anthology (\texttt{\small anthology.bib}).

\section{Length of Submission}
\label{sec:length}

The conference accepts submissions of long papers and short papers.
Long papers may consist of up to eight (8) pages of content plus unlimited pages for references.
Upon acceptance, final versions of long papers will be given one additional page -- up to nine (9) pages of content plus unlimited pages for references -- so that reviewers' comments can be taken into account.
Short papers may consist of up to four (4) pages of content, plus unlimited pages for references.
Upon acceptance, short papers will be given five (5) pages in the proceedings and unlimited pages for references. 
For both long and short papers, all illustrations and tables that are part of the main text must be accommodated within these page limits, observing the formatting instructions given in the present document.
Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.

The conference encourages the submission of additional material that is relevant to the reviewers but not an integral part of the paper.
There are two such types of material: appendices, which can be read, and non-readable supplementary materials, often data or code.
Additional material must be submitted as separate files, and must adhere to the same anonymity guidelines as the main paper.
The paper must be self-contained: it is optional for reviewers to look at the supplementary material.
Papers should not refer, for further detail, to documents, code or data resources that are not available to the reviewers.
Refer to Appendices~\ref{sec:appendix} and \ref{sec:supplemental} for further information.

Workshop chairs may have different rules for allowed length and whether supplemental material is welcome.
As always, the respective call for papers is the authoritative source.

\section{Anonymity}
As reviewing will be double-blind, papers submitted for review should not include any author information (such as names or affiliations). Furthermore, self-references that reveal the author's identity, \emph{e.g.},
\begin{quote}
We previously showed \citep{Gusfield:97} \ldots
\end{quote}
should be avoided. Instead, use citations such as 
\begin{quote}
\citet{Gusfield:97} previously showed\ldots
\end{quote}
Please do not use anonymous citations and do not include acknowledgements.
\textbf{Papers that do not conform to these requirements may be rejected without review.}

Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper.
Reviewers are generally aware that authors may present preliminary versions of their work in other venues, but will not be provided the list of previous presentations from the submission form.

Once a paper has been accepted to the conference, the camera-ready version of the paper should include the author's names and affiliations, and is allowed to use self-references.

\paragraph{\LaTeX-specific details:}
For an anonymized submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is commented out, and that you have filled in the paper ID number (assigned during the submission process on softconf) where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top of this document.
For a camera-ready submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is not commented out.

\section{Multiple Submission Policy}
Papers that have been or will be submitted to other meetings or publications must indicate this at submission time in the START submission form, and must be withdrawn from the other venues if accepted by ACL 2020. Authors of papers accepted for presentation at ACL 2020 must notify the program chairs by the camera-ready deadline as to whether the paper will be presented. We will not accept for publication or presentation the papers that overlap significantly in content or results with papers that will be (or have been) published elsewhere.

Authors submitting more than one paper to ACL 2020 must ensure that submissions do not overlap significantly (>25\%) with each other in content or results.

\section{Formatting Instructions}

Manuscripts must be in two-column format.
Exceptions to the two-column format include the title, authors' names and complete addresses, which must be centered at the top of the first page, and any full-width figures or tables (see the guidelines in Section~\ref{ssec:title-authors}).
\textbf{Type single-spaced.}
Start all pages directly under the top margin.
The manuscript should be printed single-sided and its length should not exceed the maximum page limit described in Section~\ref{sec:length}.
Pages should be numbered in the version submitted for review, but \textbf{pages should not be numbered in the camera-ready version}.

\paragraph{\LaTeX-specific details:}
The style files will generate page numbers when {\small\verb|\aclfinalcopy|} is commented out, and remove them otherwise.

\subsection{File Format}
\label{sect:pdf}

For the production of the electronic manuscript you must use Adobe's Portable Document Format (PDF).
Please make sure that your PDF file includes all the necessary fonts (especially tree diagrams, symbols, and fonts with Asian characters).
When you print or create the PDF file, there is usually an option in your printer setup to include none, all or just non-standard fonts.
Please make sure that you select the option of including ALL the fonts.
\textbf{Before sending it, test your PDF by printing it from a computer different from the one where it was created.}
Moreover, some word processors may generate very large PDF files, where each page is rendered as an image.
Such images may reproduce poorly.
In this case, try alternative ways to obtain the PDF.
One way on some systems is to install a driver for a postscript printer, send your document to the printer specifying ``Output to a file'', then convert the file to PDF.

It is of utmost importance to specify the \textbf{A4 format} (21 cm x 29.7 cm) when formatting the paper.
Print-outs of the PDF file on A4 paper should be identical to the hardcopy version.
If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs as soon as possible.

\paragraph{\LaTeX-specific details:}
PDF files are usually produced from \LaTeX{} using the \texttt{\small pdflatex} command.
If your version of \LaTeX{} produces Postscript files, \texttt{\small ps2pdf} or \texttt{\small dvipdf} can convert these to PDF.
To ensure A4 format in \LaTeX, use the command {\small\verb|\special{papersize=210mm,297mm}|}
in the \LaTeX{} preamble (below the {\small\verb|\usepackage|} commands) and use \texttt{\small dvipdf} and/or \texttt{\small pdflatex}; or specify \texttt{\small -t a4} when working with \texttt{\small dvips}.

\subsection{Layout}
\label{ssec:layout}

Format manuscripts two columns to a page, in the manner these
instructions are formatted.
The exact dimensions for a page on A4 paper are:

\begin{itemize}
\item Left and right margins: 2.5 cm
\item Top margin: 2.5 cm
\item Bottom margin: 2.5 cm
\item Column width: 7.7 cm
\item Column height: 24.7 cm
\item Gap between columns: 0.6 cm
\end{itemize}

\noindent Papers should not be submitted on any other paper size.
If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs above as soon as possible.

\subsection{Fonts}

For reasons of uniformity, Adobe's \textbf{Times Roman} font should be used.
If Times Roman is unavailable, you may use Times New Roman or \textbf{Computer Modern Roman}.

Table~\ref{font-table} specifies what font sizes and styles must be used for each type of text in the manuscript.

\begin{table}
\centering
\begin{tabular}{lrl}
\hline \textbf{Type of Text} & \textbf{Font Size} & \textbf{Style} \\ \hline
paper title & 15 pt & bold \\
author names & 12 pt & bold \\
author affiliation & 12 pt & \\
the word ``Abstract'' & 12 pt & bold \\
section titles & 12 pt & bold \\
subsection titles & 11 pt & bold \\
document text & 11 pt  &\\
captions & 10 pt & \\
abstract text & 10 pt & \\
bibliography & 10 pt & \\
footnotes & 9 pt & \\
\hline
\end{tabular}
\caption{\label{font-table} Font guide. }
\end{table}

\paragraph{\LaTeX-specific details:}
To use Times Roman in \LaTeX2e{}, put the following in the preamble:
\begin{quote}
\small
\begin{verbatim}
\usepackage{times}
\usepackage{latexsym}
\end{verbatim}
\end{quote}

\subsection{Ruler}
A printed ruler (line numbers in the left and right margins of the article) should be presented in the version submitted for review, so that reviewers may comment on particular lines in the paper without circumlocution.
The presence or absence of the ruler should not change the appearance of any other content on the page.
The camera ready copy should not contain a ruler.

\paragraph{Reviewers:}
note that the ruler measurements may not align well with lines in the paper -- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
In most cases one would expect that the approximate location will be adequate, although you can also use fractional references (\emph{e.g.}, this line ends at mark $295.5$).

\paragraph{\LaTeX-specific details:}
The style files will generate the ruler when {\small\verb|\aclfinalcopy|} is commented out, and remove it otherwise.

\subsection{Title and Authors}
\label{ssec:title-authors}

Center the title, author's name(s) and affiliation(s) across both columns.
Do not use footnotes for affiliations.
Place the title centered at the top of the first page, in a 15-point bold font.
Long titles should be typed on two lines without a blank line intervening.
Put the title 2.5 cm from the top of the page, followed by a blank line, then the author's names(s), and the affiliation on the following line.
Do not use only initials for given names (middle initials are allowed).
Do not format surnames in all capitals (\emph{e.g.}, use ``Mitchell'' not ``MITCHELL'').
Do not format title and section headings in all capitals except for proper names (such as ``BLEU'') that are
conventionally in all capitals.
The affiliation should contain the author's complete address, and if possible, an electronic mail address.

The title, author names and addresses should be completely identical to those entered to the electronical paper submission website in order to maintain the consistency of author information among all publications of the conference.
If they are different, the publication chairs may resolve the difference without consulting with you; so it is in your own interest to double-check that the information is consistent.

Start the body of the first page 7.5 cm from the top of the page.
\textbf{Even in the anonymous version of the paper, you should maintain space for names and addresses so that they will fit in the final (accepted) version.}

\subsection{Abstract}
Use two-column format when you begin the abstract.
Type the abstract at the beginning of the first column.
The width of the abstract text should be smaller than the
width of the columns for the text in the body of the paper by 0.6 cm on each side.
Center the word \textbf{Abstract} in a 12 point bold font above the body of the abstract.
The abstract should be a concise summary of the general thesis and conclusions of the paper.
It should be no longer than 200 words.
The abstract text should be in 10 point font.

\subsection{Text}
Begin typing the main body of the text immediately after the abstract, observing the two-column format as shown in the present document.

Indent 0.4 cm when starting a new paragraph.

\subsection{Sections}

Format section and subsection headings in the style shown on the present document.
Use numbered sections (Arabic numerals) to facilitate cross references.
Number subsections with the section number and the subsection number separated by a dot, in Arabic numerals.

\subsection{Footnotes}
Put footnotes at the bottom of the page and use 9 point font.
They may be numbered or referred to by asterisks or other symbols.\footnote{This is how a footnote should appear.}
Footnotes should be separated from the text by a line.\footnote{Note the line separating the footnotes from the text.}

\subsection{Graphics}

Place figures, tables, and photographs in the paper near where they are first discussed, rather than at the end, if possible.
Wide illustrations may run across both columns.
Color is allowed, but adhere to Section~\ref{ssec:accessibility}'s guidelines on accessibility.

\paragraph{Captions:}
Provide a caption for every illustration; number each one sequentially in the form:
``Figure 1. Caption of the Figure.''
``Table 1. Caption of the Table.''
Type the captions of the figures and tables below the body, using 10 point text.
Captions should be placed below illustrations.
Captions that are one line are centered (see Table~\ref{font-table}).
Captions longer than one line are left-aligned (see Table~\ref{tab:accents}).

\begin{table}
\centering
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\"a}| & {\"a} \\
\verb|{\^e}| & {\^e} \\
\verb|{\`i}| & {\`i} \\ 
\verb|{\.I}| & {\.I} \\ 
\verb|{\o}| & {\o} \\
\verb|{\'u}| & {\'u}  \\ 
\verb|{\aa}| & {\aa}  \\\hline
\end{tabular}
\begin{tabular}{lc}
\hline
\textbf{Command} & \textbf{Output}\\
\hline
\verb|{\c c}| & {\c c} \\ 
\verb|{\u g}| & {\u g} \\ 
\verb|{\l}| & {\l} \\ 
\verb|{\~n}| & {\~n} \\ 
\verb|{\H o}| & {\H o} \\ 
\verb|{\v r}| & {\v r} \\ 
\verb|{\ss}| & {\ss} \\
\hline
\end{tabular}
\caption{Example commands for accented characters, to be used in, \emph{e.g.}, \BibTeX\ names.}\label{tab:accents}
\end{table}

\paragraph{\LaTeX-specific details:}
The style files are compatible with the caption and subcaption packages; do not add optional arguments.
\textbf{Do not override the default caption sizes.}

\subsection{Hyperlinks}
Within-document and external hyperlinks are indicated with Dark Blue text, Color Hex \#000099.

\subsection{Citations}
Citations within the text appear in parentheses as~\citep{Gusfield:97} or, if the author's name appears in the text itself, as \citet{Gusfield:97}.
Append lowercase letters to the year in cases of ambiguities.  
Treat double authors as in~\citep{Aho:72}, but write as in~\citep{Chandra:81} when more than two authors are involved. Collapse multiple citations as in~\citep{Gusfield:97,Aho:72}.

Refrain from using full citations as sentence constituents.
Instead of
\begin{quote}
  ``\citep{Gusfield:97} showed that ...''
\end{quote}
write
\begin{quote}
``\citet{Gusfield:97} showed that ...''
\end{quote}

\begin{table*}
\centering
\begin{tabular}{lll}
\hline
\textbf{Output} & \textbf{natbib command} & \textbf{Old ACL-style command}\\
\hline
\citep{Gusfield:97} & \small\verb|\citep| & \small\verb|\cite| \\
\citealp{Gusfield:97} & \small\verb|\citealp| & no equivalent \\
\citet{Gusfield:97} & \small\verb|\citet| & \small\verb|\newcite| \\
\citeyearpar{Gusfield:97} & \small\verb|\citeyearpar| & \small\verb|\shortcite| \\
\hline
\end{tabular}
\caption{\label{citation-guide}
Citation commands supported by the style file.
The style is based on the natbib package and supports all natbib citation commands.
It also supports commands defined in previous ACL style files for compatibility.
}
\end{table*}

\paragraph{\LaTeX-specific details:}
Table~\ref{citation-guide} shows the syntax supported by the style files.
We encourage you to use the natbib styles.
You can use the command {\small\verb|\citet|} (cite in text) to get ``author (year)'' citations as in \citet{Gusfield:97}.
You can use the command {\small\verb|\citep|} (cite in parentheses) to get ``(author, year)'' citations as in \citep{Gusfield:97}.
You can use the command {\small\verb|\citealp|} (alternative cite without  parentheses) to get ``author year'' citations (which is useful for  using citations within parentheses, as in \citealp{Gusfield:97}).

\subsection{References}
Gather the full set of references together under the heading \textbf{References}; place the section before any Appendices. 
Arrange the references alphabetically by first author, rather than by order of occurrence in the text.

Provide as complete a citation as possible, using a consistent format, such as the one for \emph{Computational Linguistics\/} or the one in the  \emph{Publication Manual of the American 
Psychological Association\/}~\citep{APA:83}.
Use full names for authors, not just initials.

Submissions should accurately reference prior and related work, including code and data.
If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced.
If multiple versions of a piece of prior work exist, the one used by the authors should be referenced.
Authors should not rely on automated citation indices to provide accurate references for prior and related work.

The following text cites various types of articles so that the references section of the present document will include them.
\begin{itemize}
\item Example article in journal: \citep{Ando2005}.
\item Example article in proceedings, with location: \citep{borschinger-johnson-2011-particle}.
\item Example article in proceedings, without location: \citep{andrew2007scalable}.
\item Example arxiv paper: \citep{rasooli-tetrault-2015}. 
\end{itemize}

\paragraph{\LaTeX-specific details:}
The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
If your own bib file is named \texttt{\small acl2020.bib}, then placing the following before any appendices in your \LaTeX{}  file will generate the references section for you:
\begin{quote}\small
\verb|\bibliographystyle{acl_natbib}|\\
\verb|\bibliography{acl2020}|
\end{quote}

You can obtain the complete ACL Anthology as a Bib\TeX\ file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
To include both the anthology and your own bib file, use the following instead of the above.
\begin{quote}\small
\verb|\bibliographystyle{acl_natbib}|\\
\verb|\bibliography{anthology,acl2020}|
\end{quote}

\subsection{Digital Object Identifiers}
As part of our work to make ACL materials more widely used and cited outside of our discipline, ACL has registered as a CrossRef member, as a registrant of Digital Object Identifiers (DOIs), the standard for registering permanent URNs for referencing scholarly materials.

All camera-ready references are required to contain the appropriate DOIs (or as a second resort, the hyperlinked ACL Anthology Identifier) to all cited works.
Appropriate records should be found for most materials in the current ACL Anthology at \url{http://aclanthology.info/}.
As examples, we cite \citep{goodman-etal-2016-noise} to show you how papers with a DOI will appear in the bibliography.
We cite \citep{harper-2014-learning} to show how papers without a DOI but with an ACL Anthology Identifier will appear in the bibliography.

\paragraph{\LaTeX-specific details:}
Please ensure that you use Bib\TeX\ records that contain DOI or URLs for any of the ACL materials that you reference.
If the Bib\TeX{} file contains DOI fields, the paper title in the references section will appear as a hyperlink to the DOI, using the hyperref \LaTeX{} package.

\subsection{Appendices}
Appendices, if any, directly follow the text and the
references (but only in the camera-ready; see Appendix~\ref{sec:appendix}).
Letter them in sequence and provide an informative title:
\textbf{Appendix A. Title of Appendix}.

\section{Accessibility}
\label{ssec:accessibility}

In an effort to accommodate people who are color-blind (as well as those printing to paper), grayscale readability is strongly encouraged.
Color is not forbidden, but authors should ensure that tables and figures do not rely solely on color to convey critical distinctions.
A simple criterion:
All curves and points in your figures should be clearly distinguishable without color.

\section{Translation of non-English Terms}

It is also advised to supplement non-English characters and terms with appropriate transliterations and/or translations since not all readers understand all such characters and terms.
Inline transliteration or translation can be represented in the order of:
\begin{center}
\begin{tabular}{c}
original-form \\
transliteration \\
``translation''
\end{tabular}
\end{center}

\section{\LaTeX{} Compilation Issues}
You may encounter the following error during compilation: 
\begin{quote}
{\small\verb|\pdfendlink|} ended up in different nesting level than {\small\verb|\pdfstartlink|}.
\end{quote}
This happens when \texttt{\small pdflatex} is used and a citation splits across a page boundary.
To fix this, the style file contains a patch consisting of two lines:
%% (1) {\small\verb|\RequirePackage{etoolbox}|} (line 455 in \texttt{\small acl2020.sty}), and
(2) A long line below (line 456 in \texttt{\small acl2020.sty}).

If you still encounter compilation issues even with the patch enabled, disable the patch by commenting the two lines, and then disable the \texttt{\small hyperref} package by loading the style file with the \texttt{\small nohyperref} option:

\noindent
{\small\verb|\usepackage[nohyperref]{acl2020}|}

\noindent
Then recompile, find the problematic citation, and rewrite the sentence containing the citation. (See, {\em e.g.}, \url{http://tug.org/errors.html})

\section*{Acknowledgments}

The acknowledgments should go immediately before the references. Do not number the acknowledgments section.
Do not include this section when submitting your paper for review.

\bibliography{anthology,acl2020}
\bibliographystyle{acl_natbib}

\appendix

\section{Appendices}
\label{sec:appendix}
Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
Upon acceptance, the appendices come after the references, as shown here.

\paragraph{\LaTeX-specific details:}
Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.

\section{Supplemental Material}
\label{sec:supplemental}
Submissions may include non-readable supplementary material used in the work and described in the paper.
Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.

Nonetheless, supplementary material should be supplementary (rather than central) to the paper.
\textbf{Submissions that misuse the supplementary material may be rejected without review.}
Supplementary material may include explanations or details of proofs or derivations that do not fit into the paper, lists of
features or feature templates, sample inputs and outputs for a system, pseudo-code or source code, and data.
(Source code and data should be separate uploads, rather than part of the paper).

The paper should not rely on the supplementary material: while the paper may refer to and cite the supplementary material and the supplementary material will be available to the reviewers, they will not be asked to review the supplementary material.

\end{document}

### 2022-09-12 paper.tex
Added paper in word format

@@
 
-\title{Instructions for ACL 2020 Proceedings}
+\title{Multiple Sclerosis Diagnosis from Natural Language Processing of Patient Freetext Data}
 
@@
 \begin{abstract}
-This document contains the instructions for preparing a manuscript for the proceedings of ACL 2020.
-The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
-These instructions should be used for both papers submitted for review and for final versions of accepted papers.
-Authors are asked to conform to all the directions reported in this document.
+Abstract here
 \end{abstract}
-
-\section{Credits}
-
-This document has been adapted
-by Steven Bethard, Ryan Cotterrell and Rui Yan
-from the instructions for earlier ACL and NAACL proceedings, including those for 
-ACL 2019 by Douwe Kiela and Ivan Vuli\'{c},
-NAACL 2019 by Stephanie Lukin and Alla Roskovskaya, 
-ACL 2018 by Shay Cohen, Kevin Gimpel, and Wei Lu, 
-NAACL 2018 by Margaret Michell and Stephanie Lukin,
-2017/2018 (NA)ACL bibtex suggestions from Jason Eisner,
-ACL 2017 by Dan Gildea and Min-Yen Kan, 
-NAACL 2017 by Margaret Mitchell, 
-ACL 2012 by Maggie Li and Michael White, 
-ACL 2010 by Jing-Shing Chang and Philipp Koehn, 
-ACL 2008 by Johanna D. Moore, Simone Teufel, James Allan, and Sadaoki Furui, 
-ACL 2005 by Hwee Tou Ng and Kemal Oflazer, 
-ACL 2002 by Eugene Charniak and Dekang Lin, 
-and earlier ACL and EACL formats written by several people, including
-John Chen, Henry S. Thompson and Donald Walker.
-Additional elements were taken from the formatting instructions of the \emph{International Joint Conference on Artificial Intelligence} and the \emph{Conference on Computer Vision and Pattern Recognition}.
 
@@
 
-The following instructions are directed to authors of papers submitted to ACL 2020 or accepted for publication in its proceedings.
-All authors are required to adhere to these specifications.
-Authors are required to provide a Portable Document Format (PDF) version of their papers.
-\textbf{The proceedings are designed for printing on A4 paper.}
+\section{Related work}
 
-\section{Electronically-available resources}
-
-ACL provides this description and accompanying style files at
-\begin{quote}
-\url{http://acl2020.org/downloads/acl2020-templates.zip}
-\end{quote}
-We strongly recommend the use of these style files, which have been appropriately tailored for the ACL 2020 proceedings.
-
-\paragraph{\LaTeX-specific details:}
-The templates include the \LaTeX2e{} source (\texttt{\small acl2020.tex}),
-the \LaTeX2e{} style file used to format it (\texttt{\small acl2020.sty}),
-an ACL bibliography style (\texttt{\small acl\_natbib.bst}),
-an example bibliography (\texttt{\small acl2020.bib}),
-and the bibliography for the ACL Anthology (\texttt{\small anthology.bib}).
-
-\section{Length of Submission}
+\section{Data}
 \label{sec:length}
 
-The conference accepts submissions of long papers and short papers.
-Long papers may consist of up to eight (8) pages of content plus unlimited pages for references.
-Upon acceptance, final versions of long papers will be given one additional page -- up to nine (9) pages of content plus unlimited pages for references -- so that reviewers' comments can be taken into account.
-Short papers may consist of up to four (4) pages of content, plus unlimited pages for references.
-Upon acceptance, short papers will be given five (5) pages in the proceedings and unlimited pages for references. 
-For both long and short papers, all illustrations and tables that are part of the main text must be accommodated within these page limits, observing the formatting instructions given in the present document.
-Papers that do not conform to the specified length and formatting requirements are subject to be rejected without review.
+\subsection{Dataset construction}
 
-The conference encourages the submission of additional material that is relevant to the reviewers but not an integral part of the paper.
-There are two such types of material: appendices, which can be read, and non-readable supplementary materials, often data or code.
-Additional material must be submitted as separate files, and must adhere to the same anonymity guidelines as the main paper.
-The paper must be self-contained: it is optional for reviewers to look at the supplementary material.
-Papers should not refer, for further detail, to documents, code or data resources that are not available to the reviewers.
-Refer to Appendices~\ref{sec:appendix} and \ref{sec:supplemental} for further information.
+\subsection{Ethics and privacy}
 
-Workshop chairs may have different rules for allowed length and whether supplemental material is welcome.
-As always, the respective call for papers is the authoritative source.
+\section{Datset Analysis}
 
-\section{Anonymity}
-As reviewing will be double-blind, papers submitted for review should not include any author information (such as names or affiliations).
-Furthermore, self-references that reveal the author's identity, \emph{e.g.},
-\begin{quote}
-We previously showed \citep{Gusfield:97} \ldots
-\end{quote}
-should be avoided. Instead, use citations such as 
-\begin{quote}
-\citet{Gusfield:97} previously showed\ldots
-\end{quote}
-Please do not use anonymous citations and do not include acknowledgements.
-\textbf{Papers that do not conform to these requirements may be rejected without review.}
+\section{Experiments}
 
-Any preliminary non-archival versions of submitted papers should be listed in the submission form but not in the review version of the paper.
-Reviewers are generally aware that authors may present preliminary versions of their work in other venues, but will not be provided the list of previous presentations from the submission form.
-
-Once a paper has been accepted to the conference, the camera-ready version of the paper should include the author's names and affiliations, and is allowed to use self-references.
-
-\paragraph{\LaTeX-specific details:}
-For an anonymized submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is commented out, and that you have filled in the paper ID number (assigned during the submission process on softconf) where {\small\verb|***|} appears in the {\small\verb|\def\aclpaperid{***}|} definition at the top of this document.
-For a camera-ready submission, ensure that {\small\verb|\aclfinalcopy|} at the top of this document is not commented out.
-
-\section{Multiple Submission Policy}
-Papers that have been or will be submitted to other meetings or publications must indicate this at submission time in the START submission form, and must be withdrawn from the other venues if accepted by ACL 2020.
-Authors of papers accepted for presentation at ACL 2020 must notify the program chairs by the camera-ready deadline as to whether the paper will be presented.
-We will not accept for publication or presentation the papers that overlap significantly in content or results with papers that will be (or have been) published elsewhere.
-
-Authors submitting more than one paper to ACL 2020 must ensure that submissions do not overlap significantly (>25\%) with each other in content or results.
-
-\section{Formatting Instructions}
-
-Manuscripts must be in two-column format.
-Exceptions to the two-column format include the title, authors' names and complete addresses, which must be centered at the top of the first page, and any full-width figures or tables (see the guidelines in Section~\ref{ssec:title-authors}).
-\textbf{Type single-spaced.}
-Start all pages directly under the top margin.
-The manuscript should be printed single-sided and its length should not exceed the maximum page limit described in Section~\ref{sec:length}.
-Pages should be numbered in the version submitted for review, but \textbf{pages should not be numbered in the camera-ready version}.
-
-\paragraph{\LaTeX-specific details:}
-The style files will generate page numbers when {\small\verb|\aclfinalcopy|} is commented out, and remove them otherwise.
-
-\subsection{File Format}
-\label{sect:pdf}
-
-For the production of the electronic manuscript you must use Adobe's Portable Document Format (PDF).
-Please make sure that your PDF file includes all the necessary fonts (especially tree diagrams, symbols, and fonts with Asian characters).
-When you print or create the PDF file, there is usually an option in your printer setup to include none, all or just non-standard fonts.
-Please make sure that you select the option of including ALL the fonts.
-\textbf{Before sending it, test your PDF by printing it from a computer different from the one where it was created.}
-Moreover, some word processors may generate very large PDF files, where each page is rendered as an image.
-Such images may reproduce poorly.
-In this case, try alternative ways to obtain the PDF.
-One way on some systems is to install a driver for a postscript printer, send your document to the printer specifying ``Output to a file'', then convert the file to PDF.
-
-It is of utmost importance to specify the \textbf{A4 format} (21 cm x 29.7 cm) when formatting the paper.
-Print-outs of the PDF file on A4 paper should be identical to the hardcopy version.
-If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs as soon as possible.
-
-\paragraph{\LaTeX-specific details:}
-PDF files are usually produced from \LaTeX{} using the \texttt{\small pdflatex} command.
-If your version of \LaTeX{} produces Postscript files, \texttt{\small ps2pdf} or \texttt{\small dvipdf} can convert these to PDF.
-To ensure A4 format in \LaTeX, use the command {\small\verb|\special{papersize=210mm,297mm}|}
-in the \LaTeX{} preamble (below the {\small\verb|\usepackage|} commands) and use \texttt{\small dvipdf} and/or \texttt{\small pdflatex}; or specify \texttt{\small -t a4} when working with \texttt{\small dvips}.
-
-\subsection{Layout}
-\label{ssec:layout}
-
-Format manuscripts two columns to a page, in the manner these
-instructions are formatted.
-The exact dimensions for a page on A4 paper are:
-
-\begin{itemize}
-\item Left and right margins: 2.5 cm
-\item Top margin: 2.5 cm
-\item Bottom margin: 2.5 cm
-\item Column width: 7.7 cm
-\item Column height: 24.7 cm
-\item Gap between columns: 0.6 cm
-\end{itemize}
-
-\noindent Papers should not be submitted on any other paper size.
-If you cannot meet the above requirements about the production of your electronic submission, please contact the publication chairs above as soon as possible.
-
-\subsection{Fonts}
-
-For reasons of uniformity, Adobe's \textbf{Times Roman} font should be used.
-If Times Roman is unavailable, you may use Times New Roman or \textbf{Computer Modern Roman}.
-
-Table~\ref{font-table} specifies what font sizes and styles must be used for each type of text in the manuscript.
-
-\begin{table}
-\centering
-\begin{tabular}{lrl}
-\hline \textbf{Type of Text} & \textbf{Font Size} & \textbf{Style} \\ \hline
-paper title & 15 pt & bold \\
-author names & 12 pt & bold \\
-author affiliation & 12 pt & \\
-the word ``Abstract'' & 12 pt & bold \\
-section titles & 12 pt & bold \\
-subsection titles & 11 pt & bold \\
-document text & 11 pt  &\\
-captions & 10 pt & \\
-abstract text & 10 pt & \\
-bibliography & 10 pt & \\
-footnotes & 9 pt & \\
-\hline
-\end{tabular}
-\caption{\label{font-table} Font guide. }
-\end{table}
-
-\paragraph{\LaTeX-specific details:}
-To use Times Roman in \LaTeX2e{}, put the following in the preamble:
-\begin{quote}
-\small
-\begin{verbatim}
-\usepackage{times}
-\usepackage{latexsym}
-\end{verbatim}
-\end{quote}
-
-\subsection{Ruler}
-A printed ruler (line numbers in the left and right margins of the article) should be presented in the version submitted for review, so that reviewers may comment on particular lines in the paper without circumlocution.
-The presence or absence of the ruler should not change the appearance of any other content on the page.
-The camera ready copy should not contain a ruler.
-
-\paragraph{Reviewers:}
-note that the ruler measurements may not align well with lines in the paper -- this turns out to be very difficult to do well when the paper contains many figures and equations, and, when done, looks ugly.
-In most cases one would expect that the approximate location will be adequate, although you can also use fractional references (\emph{e.g.}, this line ends at mark $295.5$).
-
-\paragraph{\LaTeX-specific details:}
-The style files will generate the ruler when {\small\verb|\aclfinalcopy|} is commented out, and remove it otherwise.
-
-\subsection{Title and Authors}
-\label{ssec:title-authors}
-
-Center the title, author's name(s) and affiliation(s) across both columns.
-Do not use footnotes for affiliations.
-Place the title centered at the top of the first page, in a 15-point bold font.
-Long titles should be typed on two lines without a blank line intervening.
-Put the title 2.5 cm from the top of the page, followed by a blank line, then the author's names(s), and the affiliation on the following line.
-Do not use only initials for given names (middle initials are allowed).
-Do not format surnames in all capitals (\emph{e.g.}, use ``Mitchell'' not ``MITCHELL'').
-Do not format title and section headings in all capitals except for proper names (such as ``BLEU'') that are
-conventionally in all capitals.
-The affiliation should contain the author's complete address, and if possible, an electronic mail address.
-
-The title, author names and addresses should be completely identical to those entered to the electronical paper submission website in order to maintain the consistency of author information among all publications of the conference.
-If they are different, the publication chairs may resolve the difference without consulting with you; so it is in your own interest to double-check that the information is consistent.
-
-Start the body of the first page 7.5 cm from the top of the page.
-\textbf{Even in the anonymous version of the paper, you should maintain space for names and addresses so that they will fit in the final (accepted) version.}
-
-\subsection{Abstract}
-Use two-column format when you begin the abstract.
-Type the abstract at the beginning of the first column.
-The width of the abstract text should be smaller than the
-width of the columns for the text in the body of the paper by 0.6 cm on each side.
-Center the word \textbf{Abstract} in a 12 point bold font above the body of the abstract.
-The abstract should be a concise summary of the general thesis and conclusions of the paper.
-It should be no longer than 200 words.
-The abstract text should be in 10 point font.
-
-\subsection{Text}
-Begin typing the main body of the text immediately after the abstract, observing the two-column format as shown in the present document.
-
-Indent 0.4 cm when starting a new paragraph.
-
-\subsection{Sections}
-
-Format section and subsection headings in the style shown on the present document.
-Use numbered sections (Arabic numerals) to facilitate cross references.
-Number subsections with the section number and the subsection number separated by a dot, in Arabic numerals.
-
-\subsection{Footnotes}
-Put footnotes at the bottom of the page and use 9 point font.
-They may be numbered or referred to by asterisks or other symbols.\footnote{This is how a footnote should appear.}
-Footnotes should be separated from the text by a line.\footnote{Note the line separating the footnotes from the text.}
-
-\subsection{Graphics}
-
-Place figures, tables, and photographs in the paper near where they are first discussed, rather than at the end, if possible.
-Wide illustrations may run across both columns.
-Color is allowed, but adhere to Section~\ref{ssec:accessibility}'s guidelines on accessibility.
-
-\paragraph{Captions:}
-Provide a caption for every illustration; number each one sequentially in the form:
-``Figure 1. Caption of the Figure.''
-``Table 1. Caption of the Table.''
-Type the captions of the figures and tables below the body, using 10 point text.
-Captions should be placed below illustrations.
-Captions that are one line are centered (see Table~\ref{font-table}).
-Captions longer than one line are left-aligned (see Table~\ref{tab:accents}).
-
-\begin{table}
-\centering
-\begin{tabular}{lc}
-\hline
-\textbf{Command} & \textbf{Output}\\
-\hline
-\verb|{\"a}| & {\"a} \\
-\verb|{\^e}| & {\^e} \\
-\verb|{\`i}| & {\`i} \\ 
-\verb|{\.I}| & {\.I} \\ 
-\verb|{\o}| & {\o} \\
-\verb|{\'u}| & {\'u}  \\ 
-\verb|{\aa}| & {\aa}  \\\hline
-\end{tabular}
-\begin{tabular}{lc}
-\hline
-\textbf{Command} & \textbf{Output}\\
-\hline
-\verb|{\c c}| & {\c c} \\ 
-\verb|{\u g}| & {\u g} \\ 
-\verb|{\l}| & {\l} \\ 
-\verb|{\~n}| & {\~n} \\ 
-\verb|{\H o}| & {\H o} \\ 
-\verb|{\v r}| & {\v r} \\ 
-\verb|{\ss}| & {\ss} \\
-\hline
-\end{tabular}
-\caption{Example commands for accented characters, to be used in, \emph{e.g.}, \BibTeX\ names.}\label{tab:accents}
-\end{table}
-
-\paragraph{\LaTeX-specific details:}
-The style files are compatible with the caption and subcaption packages; do not add optional arguments.
-\textbf{Do not override the default caption sizes.}
-
-\subsection{Hyperlinks}
-Within-document and external hyperlinks are indicated with Dark Blue text, Color Hex \#000099.
-
-\subsection{Citations}
-Citations within the text appear in parentheses as~\citep{Gusfield:97} or, if the author's name appears in the text itself, as \citet{Gusfield:97}.
-Append lowercase letters to the year in cases of ambiguities.  
-Treat double authors as in~\citep{Aho:72}, but write as in~\citep{Chandra:81} when more than two authors are involved. Collapse multiple citations as in~\citep{Gusfield:97,Aho:72}.
-
-Refrain from using full citations as sentence constituents.
-Instead of
-\begin{quote}
-  ``\citep{Gusfield:97} showed that ...''
-\end{quote}
-write
-\begin{quote}
-``\citet{Gusfield:97} showed that ...''
-\end{quote}
-
-\begin{table*}
-\centering
-\begin{tabular}{lll}
-\hline
-\textbf{Output} & \textbf{natbib command} & \textbf{Old ACL-style command}\\
-\hline
-\citep{Gusfield:97} & \small\verb|\citep| & \small\verb|\cite| \\
-\citealp{Gusfield:97} & \small\verb|\citealp| & no equivalent \\
-\citet{Gusfield:97} & \small\verb|\citet| & \small\verb|\newcite| \\
-\citeyearpar{Gusfield:97} & \small\verb|\citeyearpar| & \small\verb|\shortcite| \\
-\hline
-\end{tabular}
-\caption{\label{citation-guide}
-Citation commands supported by the style file.
-The style is based on the natbib package and supports all natbib citation commands.
-It also supports commands defined in previous ACL style files for compatibility.
-}
-\end{table*}
-
-\paragraph{\LaTeX-specific details:}
-Table~\ref{citation-guide} shows the syntax supported by the style files.
-We encourage you to use the natbib styles.
-You can use the command {\small\verb|\citet|} (cite in text) to get ``author (year)'' citations as in \citet{Gusfield:97}.
-You can use the command {\small\verb|\citep|} (cite in parentheses) to get ``(author, year)'' citations as in \citep{Gusfield:97}.
-You can use the command {\small\verb|\citealp|} (alternative cite without  parentheses) to get ``author year'' citations (which is useful for  using citations within parentheses, as in \citealp{Gusfield:97}).
-
-\subsection{References}
-Gather the full set of references together under the heading \textbf{References}; place the section before any Appendices. 
-Arrange the references alphabetically by first author, rather than by order of occurrence in the text.
-
-Provide as complete a citation as possible, using a consistent format, such as the one for \emph{Computational Linguistics\/} or the one in the  \emph{Publication Manual of the American 
-Psychological Association\/}~\citep{APA:83}.
-Use full names for authors, not just initials.
-
-Submissions should accurately reference prior and related work, including code and data.
-If a piece of prior work appeared in multiple venues, the version that appeared in a refereed, archival venue should be referenced.
-If multiple versions of a piece of prior work exist, the one used by the authors should be referenced.
-Authors should not rely on automated citation indices to provide accurate references for prior and related work.
-
-The following text cites various types of articles so that the references section of the present document will include them.
-\begin{itemize}
-\item Example article in journal: \citep{Ando2005}.
-\item Example article in proceedings, with location: \citep{borschinger-johnson-2011-particle}.
-\item Example article in proceedings, without location: \citep{andrew2007scalable}.
-\item Example arxiv paper: \citep{rasooli-tetrault-2015}. 
-\end{itemize}
-
-\paragraph{\LaTeX-specific details:}
-The \LaTeX{} and Bib\TeX{} style files provided roughly follow the American Psychological Association format.
-If your own bib file is named \texttt{\small acl2020.bib}, then placing the following before any appendices in your \LaTeX{}  file will generate the references section for you:
-\begin{quote}\small
-\verb|\bibliographystyle{acl_natbib}|\\
-\verb|\bibliography{acl2020}|
-\end{quote}
-
-You can obtain the complete ACL Anthology as a Bib\TeX\ file from \url{https://aclweb.org/anthology/anthology.bib.gz}.
-To include both the anthology and your own bib file, use the following instead of the above.
-\begin{quote}\small
-\verb|\bibliographystyle{acl_natbib}|\\
-\verb|\bibliography{anthology,acl2020}|
-\end{quote}
-
-\subsection{Digital Object Identifiers}
-As part of our work to make ACL materials more widely used and cited outside of our discipline, ACL has registered as a CrossRef member, as a registrant of Digital Object Identifiers (DOIs), the standard for registering permanent URNs for referencing scholarly materials.
-
-All camera-ready references are required to contain the appropriate DOIs (or as a second resort, the hyperlinked ACL Anthology Identifier) to all cited works.
-Appropriate records should be found for most materials in the current ACL Anthology at \url{http://aclanthology.info/}.
-As examples, we cite \citep{goodman-etal-2016-noise} to show you how papers with a DOI will appear in the bibliography.
-We cite \citep{harper-2014-learning} to show how papers without a DOI but with an ACL Anthology Identifier will appear in the bibliography.
-
-\paragraph{\LaTeX-specific details:}
-Please ensure that you use Bib\TeX\ records that contain DOI or URLs for any of the ACL materials that you reference.
-If the Bib\TeX{} file contains DOI fields, the paper title in the references section will appear as a hyperlink to the DOI, using the hyperref \LaTeX{} package.
-
-\subsection{Appendices}
-Appendices, if any, directly follow the text and the
-references (but only in the camera-ready; see Appendix~\ref{sec:appendix}).
-Letter them in sequence and provide an informative title:
-\textbf{Appendix A. Title of Appendix}.
-
-\section{Accessibility}
-\label{ssec:accessibility}
-
-In an effort to accommodate people who are color-blind (as well as those printing to paper), grayscale readability is strongly encouraged.
-Color is not forbidden, but authors should ensure that tables and figures do not rely solely on color to convey critical distinctions.
-A simple criterion:
-All curves and points in your figures should be clearly distinguishable without color.
-
-\section{Translation of non-English Terms}
-
-It is also advised to supplement non-English characters and terms with appropriate transliterations and/or translations since not all readers understand all such characters and terms.
-Inline transliteration or translation can be represented in the order of:
-\begin{center}
-\begin{tabular}{c}
-original-form \\
-transliteration \\
-``translation''
-\end{tabular}
-\end{center}
-
-\section{\LaTeX{} Compilation Issues}
-You may encounter the following error during compilation: 
-\begin{quote}
-{\small\verb|\pdfendlink|} ended up in different nesting level than {\small\verb|\pdfstartlink|}.
-\end{quote}
-This happens when \texttt{\small pdflatex} is used and a citation splits across a page boundary.
-To fix this, the style file contains a patch consisting of two lines:
-%% (1) {\small\verb|\RequirePackage{etoolbox}|} (line 455 in \texttt{\small acl2020.sty}), and
-(2) A long line below (line 456 in \texttt{\small acl2020.sty}).
-
-If you still encounter compilation issues even with the patch enabled, disable the patch by commenting the two lines, and then disable the \texttt{\small hyperref} package by loading the style file with the \texttt{\small nohyperref} option:
-
-\noindent
-{\small\verb|\usepackage[nohyperref]{acl2020}|}
-
-\noindent
-Then recompile, find the problematic citation, and rewrite the sentence containing the citation. (See, {\em e.g.}, \url{http://tug.org/errors.html})
-
-\section*{Acknowledgments}
-
-The acknowledgments should go immediately before the references. Do not number the acknowledgments section.
-Do not include this section when submitting your paper for review.
+\section{Conclusion}
+\citep{Gusfield:97}
+\citet{Gusfield:97}
+\citep{Aho:72}
+\citep{Chandra:81}
+\citep{Gusfield:97,Aho:72}.
 
@@
 \label{sec:appendix}
-Appendices are material that can be read, and include lemmas, formulas, proofs, and tables that are not critical to the reading and understanding of the paper. 
-Appendices should be \textbf{uploaded as supplementary material} when submitting the paper for review.
-Upon acceptance, the appendices come after the references, as shown here.
-
-\paragraph{\LaTeX-specific details:}
-Use {\small\verb|\appendix|} before any appendix section to switch the section numbering over to letters.
 
@@
 \label{sec:supplemental}
-Submissions may include non-readable supplementary material used in the work and described in the paper.
-Any accompanying software and/or data should include licenses and documentation of research review as appropriate.
-Supplementary material may report preprocessing decisions, model parameters, and other details necessary for the replication of the experiments reported in the paper.
-Seemingly small preprocessing decisions can sometimes make a large difference in performance, so it is crucial to record such decisions to precisely characterize state-of-the-art methods.
-
-Nonetheless, supplementary material should be supplementary (rather than central) to the paper.
-\textbf{Submissions that misuse the supplementary material may be rejected without review.}
-Supplementary material may include explanations or details of proofs or derivations that do not fit into the paper, lists of
-features or feature templates, sample inputs and outputs for a system, pseudo-code or source code, and data.
-(Source code and data should be separate uploads, rather than part of the paper).
-
-The paper should not rely on the supplementary material: while the paper may refer to and cite the supplementary material and the supplementary material will be available to the reviewers, they will not be asked to review the supplementary material.
 

### 2022-09-12 paper.tex
Added citations

@@
 
-\title{Multiple Sclerosis Diagnosis from Natural Language Processing of Patient Freetext Data}
+\title{Multiple Sclerosis Diagnosis from Natural Language Processing of Patient Text Data}
 
@@
 \begin{abstract}
-Abstract here
 \end{abstract}
@@
 \section{Introduction}
-
+Multiple Sclerosis (MS) is a chronic, inflammatory, neurological condition that has presented itself as a significant challenge to healthcare.
+According to \citet{Walton:20}, it is estimated that 2.8 million people worldwide suffer from MS in 2020.
+Furthermore, a cure for MS still does not exist and knowledge about the condition is currently incomplete \citep{Bebo:22}.
+Thus, there is a compelling need to improve our understanding of the condition.
+\\
+\indent Specifically, one of the challenges that primary healthcare providers face is the diagnosis of MS.
+There is no single test or laboratory marker for the diagnosis of MS, and diagnosis of MS is usually done by ruling out other similar conditions \citep{Omerhoca:18}.
+Since MS can potentially cause a vast variety of symptoms, including muscle spasms, vision problems and anxiety \citep{Ghasemi:17}, accurate diagnosis of the patient seems increasingly impossible without computerized diagnostic assistance.
+\\
+\indent A solution to improve the accuracy of multiple sclerosis diagnosis can be NLP-based predictive classifiers, which take the experiences of the patient – in text format – as input.
+This method can be inexpensive yet effective because a well-trained classifier should not only be able to detect physical symptoms of MS in the text, but also be able to capture the psychological differences – at least those that can be expressed through language – between people with and without MS.
+Therefore, the aim of this study was to investigate the accuracy of NLP-based predictive models to detect multiple sclerosis from patient free text data.
+\\
+\indent Our work has the following important improvements over existing literature.
+To create our dataset, we utilize a unique approach where we combine data from social media with the data from the MSRegister database, a database of clinically diagnosed MS patients from the UK \citep{Ford:12}.
+Since the MSRegister database has a relatively large number of MS patients, with this approach we were able to create the largest ever dataset for computerized MS diagnosis from free text.
+Moreover, existing research in free text MS diagnosis is also limited because most research relies on only one type of predictive classifier.
+Thus, another way we extend prior research is by training and testing multiple classification models on the dataset and comparing their performance to get the best classifier for our use-case.
+\\
+\indent Our contributions are as follows: \emph{(i)} create the largest ever dataset for computerized MS diagnosis from free text by combining the data from the existing MSRegister dataset with newly collected social media data \emph{(ii)} perform data analysis on this newly created dataset \emph{(iii)} build and train binary classifiers on the dataset to detect multiple sclerosis from patient free text.
 \section{Related work}
-
+Natural language processing has been extensively employed in medical diagnosis in the past decade.
+\citet{Swartz:17} was able to apply natural language processing to diagnose venous thromboembolism (VTE) from radiology reports with a high degree of accuracy.
+\citet{Kolanu:20} similarly uses NLP techniques to improve identification of patients with clinically significant fractures.
+\citet{Liang:19} utilized a deep learning NLP system to extract clinically important information from electronic health records for diagnosis of paediatric diseases.
+\citet{Coppersmith:14} relied on publicly available Twitter data to create NLP-based classifiers to detect mental health disorders, including post-traumatic stress disorder (PTSD), depression, bipolar disorder, and seasonal affective disorder (SAD).
+\citet{Yang:19} was able to develop a recurrent neural network with contextual word embeddings to get state-of-the-art accuracy in extracting symptoms from the electronic health record.
+\\
+\indent Although natural language processing has been pervasively applied in medical diagnosis, prior research in NLP-based diagnosis of MS is limited.
+While \citet{Chase:17} created a predictive model for diagnosing MS from patient clinical notes, they employed a relatively small dataset of only 165 MS patients, and they only use Naïve Bayes classification as a predictive model.
+Although \citet{Koss;Joschko:22} employ NLP methods to investigate patterns in the unmet medical needs of MS patients, they do not explicitly build classification models for MS detection from text data.
+\citet{Schwab;Karlen:21} utilise the multimodal, smartphone-collected data of MS patients to a train a model to diagnose MS.
+This data also includes questionnaires, but they only use simple sentiment analysis to calculate a mood score which is then used as an input to the model – there was no further NLP analysis of the questionnaire data.
+Furthermore, they only consider deep learning as a method for diagnosing MS patients.
+\\
+\indent We extend this existing body of work by generating the largest ever dataset for computerized MS diagnosis and conducting extensive natural language processing analysis on this dataset.
+As part of this analysis, we explore multiple methods of converting text in the dataset to word vectors and we train various machine learning models on these word vectors for the diagnosis of MS.
 \section{Data}
-\label{sec:length}
-
+\label{sec:data}
+To build binary classifiers for detecting multiple sclerosis from free text, we need a dataset containing experiences of both people with and people without MS, in text format.
+In this section, we describe how such a dataset was constructed by combining the data from social media platforms with data from the MSRegister database \citep{Ford:12}.
+We then discuss the privacy and ethical issues surrounding the construction of our dataset.
 \subsection{Dataset construction}
-
+\textbf{Diagnosed group.} To get textual comments outlining the experiences of MS patients, we will utilize free text data from the MSRegister database \citep{Ford:12}.
+We chose to use this database because it provides a large, rich resource of experiences of patients diagnosed with MS, in text format.
+However, one problem of using this dataset directly for our use-case is that the experiences of the patients are recorded post MS diagnosis, which means patients often refer to their condition (that is, multiple sclerosis), in their comments.
+However, since the classifier will be used pre-diagnosis, we cannot make this classifier rely on the term “multiple sclerosis”, or any other term that only MS patients will know about.
+Therefore, we remove all clauses containing MS-related terms (footnote with list link) from patient comments.
+If every clause in a patient comment includes some MS-related term, then we omit the comment from our dataset.
+With this approach, we were able to get 6121 comments from ****** diagnosed users in our dataset.
+\\
+\indent \textbf{Control group.} To get the experiences of users who do not have MS (that is, the control group), we chose social media platforms because, like the MSRegister database, people share their experiences in text format on these platforms.
+Twitter and Reddit were chosen as the social media platforms because they are popular platforms where users often post in plain text about their general life experiences.
+Therefore, from these social media platforms, we construct two separate control groups.
+The explanation for the need for two control groups and the description of how these control groups were constructed are outlined below.
+\\
+\indent The first control group constitutes random users from Twitter and Reddit who have not mentioned the term “MS” or any related terms in their timeline.
+The dataset was constructed such that there is an equal probability for a potential control user to be selected from Twitter or from Reddit.
+Moreover, we ignored image-only posts, video-only posts, Twitter retweets and Reddit cross-posts.
+For Reddit, we added the additional restriction that the potential control group user has never posted on any MS-related subreddit (footnote).
+After identifying the users, we select random posts in their timeline to be included in our dataset.
+The number of posts we select per user is controlled such that the final user-comment distribution is kept the same as the diagnosed users in the dataset, as illustrated in Figure *******.
+Finally, as a measure to prevent posts created by bots to be included in our dataset, no more than 5 duplicate posts were allowed by the same user.
+\\
+\indent This first control group is relevant because a classifier trained using this control group can potentially be used to automatically diagnose a social media user for MS.
+However, we observed a potential problem: since social media contains a large variety of text data, including news, satire and advertisements, a good classifier will likely learn that all this text data corresponds to a person not having MS.
+Thus, although a classifier resulting from control one can be used in social media for MS diagnosis, it may still be inaccurate in clinical settings.
+To solve this problem, we need to create another control group containing experiences of patients diagnosed with another illness.
+\\
+\indent Therefore, the second control group are comments of users who have given self-reported diagnoses of diabetes on social media (both type 1 and type 2), and who, like the first control group, have not mentioned “MS” or any related terms in their timeline.
+Diabetes was chosen as the illness for the second control group because firstly, it is an incurable, chronic condition like MS, and secondly, it is relatively prevalent, so we can find enough users on social media to exactly match the number of MS-diagnosed users from the MSRegister dataset.
+The users were found by searching on Twitter and Reddit for high-precision diagnostic patterns (footnote), examples of which can be found in Figure *******.
+After identifying these users, we only include posts where the user mentions their condition (that is, diabetes), because we would expect only those experiences to be presented to a primary healthcare provider.
+Then, like what we did for the diagnosed users, we remove all clauses with the word “diabetes” from the text, since the classifier will be used pre-diagnosis, and we cannot make the classifier rely on the term “diabetes” for classifying patients who do not have MS.
+\\
+\indent For both the control groups, the number of comments and the user-comment distribution was kept the same as the diagnosed users.
+However, the age and gender of the users could not be controlled for since APIs of social media platforms do not provide this data.
 \subsection{Ethics and privacy}
-
+The risks associated with our data collection and data access methods are minimal.
+All the posts collected from Twitter and Reddit were publicly available through the Twitter and Reddit API respectively.
+We replaced social media usernames with user identifier codes to anonymise their identity.
+Although the MSRegister database contains identifiable information, including the gender and date of birth of the patients, this database was accessed through a secure virtual desktop environment, so the identifiable information remains private.
+For both the patients in the MSRegister database and the social media users, we made no attempt identify the users with other external sources of information.
+Therefore, this research was conducted in compliance to the GDBR guidelines of data protection \citep{GDBR:16}.
 \section{Datset Analysis}
-
+To increase our understanding of the newly created dataset, we started by conducting some preliminary data analysis on our dataset. \\
+\indent To begin with, we created word clouds from the text given by the MS-diagnosed users (Figure ******a), the generic control one users (Figure ******b), and the diabetes control two users (Figure *****c).
+Before creating each of these word clouds, the text was made lowercase, stop words were removed from the text, and the text was tokenized.
+\\
+\indent Inspecting the word clouds, we see that it is consistent with our expectations of the various parts of the dataset.
+Words prevalent in the MS-diagnosed group that are absent in the other groups are ‘fatigue’, ‘walking’, ‘pain’, ‘support’ and ‘wheelchair’, which are words representing symptoms of MS \citep{Gustavsen:21}.
+Common words in the diabetes control group are ‘diet’, ‘weight’, ‘eating’, 'sugar', and 'blood', which is as expected given the symptoms of diabetes \citep{Ramachandran:14}.
+The generic control group contains common words used in social media, such as ‘love’, ‘game’, ‘people’ and ‘one’.
+Words used commonly in the English language, like ‘time’ and ‘get’ were present in all three sections of the dataset.
+Another notable point is that the word ‘ms’ is not present in the MS-diagnosed group and the word ‘diabetes’ is not present in the diabetes control group.
+This is consistent with the dataset construction method because all clauses with the word ‘ms’ were removed from the MS-diagnosed dataset and similarly all clauses with the word ‘diabetes’ were removed from the diabetes control group, as explained in the ‘Dataset construction’ section above.
+\\
+\indent In addition to generating the word clouds for the dataset, we decided to count the average number of tokens per comment for each part of the dataset.
+The results of this investigation are shown in Table **********.
+We observe that the average number of tokens is the greatest for the diabetes control group, lower for the MS-diagnosed control group and lowest for the generic social media control group.
+Since sentence length varies significantly across the dataset, we need to ensure that the classifiers we train on the dataset do not rely only on the length of the comment for text classification.
+The implications of this difference are further discussed in the next section.
 \section{Experiments}
-
+In order to understand which classifier is the best for detecting MS, we experimented several ways to convert text to word vectors and we applied various classification models on these word vectors.
+\\
+\indent However, before conducting any experiments, we pre-processed the dataset as follows.
+We removed any punctuation and URLs from the free text and made all the characters lowercase.
+To handle hashtags, tags, and subreddit names in the text collected from social media, we removed the characters ‘\#’, ‘@’ and ‘r/’ from the start of every word in the free text, if the word started with any of those characters.
+Finally, we tokenized, lemmatized and removed stop words (footnote) from the text in the database.
+\\
+\indent After pre-processing, we explored three ways of converting the pre-processed text into word vectors: bag of words (BoW), tf-idf weighted BoW, and word embeddings.
+For BoW and tf-idf weighted BoW, the vocabulary was set to 1600.
+Therefore, the dimension of every word vector was 1600.
+For word embeddings, we employed word2vec embeddings pretrained using the continuous bag-of-words (CBOW) method on the Google News dataset \citep{Mikolav:13}.
+The dimension of each of these pretrained word vectors was 300.
+For each of the classifiers below (except RNN and LSTM), we also average the word embeddings of all the tokens in every comment to get an embedding for each comment.
+We then use this embedding as input to the model.
+\\
+\indent The dataset was then split into 80\% training dataset and a 20\% testing dataset.
+For each of the three methods to convert text into word vectors, we train and test the dataset on the following classifiers: \\
+\indent \textbf{Logistic Regression.} We started by training a simple logistic regression model on the word vectors. \\
+\indent \textbf{Naïve Bayes.} For the BoW vectors and the tf-idf weighted BoW, we train the probabilistic multinomial Naïve Bayes classifier.
+Since the multinomial Naïve Bayes classifier expects positive word vectors and our word embeddings contain values from -1 to 1, we normalize the word embedding values to the range 0 to 1 and then train the classifier.
+\\
+\indent \textbf{K-Nearest Neighbours (KNN).} For the KNN classifier, we set the value k to 1, 2, 3, 5, 8, 10, and 100. The best accuracy was then recorded in Table ***. \\
+\indent \textbf{Neural Network.} We decided to investigate both a single-layer neural network and two-layer neural network.
+We set the number of epochs to 10 and batch size to 64.
+In the final layer, we use the sigmoid activation function, and for non-output layers, we tried both the ReLU and tanh activation function.
+For the two-layer neural network, we set the number of neurons in the hidden layer to 50, 100 and 200.
+After testing these hyperparameters, the best accuracy was then recorded in Table ****.
+\\
+\indent \textbf{Recurrent Neural Network (RNN).} Since we need an embedding for each word for the RNN, BoW and tfidf-weighted BoW cannot be used for this model.
+Furthermore, the RNN, by nature of being a sequential model, exemplifies the difference between input sequence lengths.
+Since we know that the average comment length varies considerably in different sections of the dataset, as shown in Table **** in Section ****, for RNNs we particularly need to make sure that the classifier does not rely only on the length of the text for classification.
+Therefore, we set the number of RNN units to minimum of the average comment lengths of the datasets in question (rounded up).
+Accordingly, from the values in Table **** in Section ****, we set the number of RNN units for diagnosed users vs.
+control one (generic) to be 15 and diagnosed users vs.
+control two (diabetes) to 30.
+Then, any comments with longer lengths were truncated to the number of RNN units.
+This strategy ensures that the classifier relies on the content of the text rather than its length.
+Lastly, we set the number of epochs to 10 and batch size to 64 before training.
+\\
+\indent \textbf{Long Short-Term Memory Network (LSTM).} The hyperparameters used for the LSTM model were kept the same as the RNN, and for the same reasons as the RNN.
+BoW and tfidf-weighted BoW could not be used for this model as well, and the number of LSTM units was again chosen to be 15 with control one and 30 with control two.
+The number of epochs was set to 10 and batch size to 64.
+\\
+\indent The results for each of these classification models are reported in Table ****. \\
+****Tables \\
+\indent Overall, for control one, word embeddings with a two-layer neural network obtained the best accuracy of 94.3\%.
+With control two, tf-idf-weighted BoW with a Naïve Bayes classifier had the best accuracy of 92.4\%.
+We believe that richer, more complicated models like RNNs and LSTMs did not do as well because they must have overfit on the training set, which eventually led to a lower accuracy on the test set.
+\\
+\indent In general, our experiments with control one had higher accuracy than with control two.
+Therefore, we conclude that classifiers find it easier to distinguish between generic social media text and the experiences of MS patients rather than distinguish between experiences of diabetes patients and MS patients.
+\\
+\indent Another interesting observation is that for control two, word embeddings always performed worse than BoW or tf-idf-weighted BoW, even though word embeddings are usually known for having more semantic richness than BoW models \citep{Mikolav:13}.
+This result can be explained by the fact that BoW models give more weight to particular words, which likely correspond to symptoms of MS and diabetes in this case.
+On the other hand, word embeddings cannot distinguish that well between the MS-diagnosed user group and the diabetes control because comments from both these groups contain medical terminology and are thus likely to have similar word embeddings.
 \section{Conclusion}
-\citep{Gusfield:97}
-\citet{Gusfield:97}
-\citep{Aho:72}
-\citep{Chandra:81}
-\citep{Gusfield:97,Aho:72}.
-
+By employing a novel approach combining social media data with the MSRegister dataset of MS patients in the UK, we were able to create the largest ever dataset for computerized diagnosis for MS.
+We trained multiple different models on this dataset, and we were able to achieve a maximum accuracy of 94.3\% when classifying experiences of MS patients against generic social media text data and a maximum accuracy of 92.4\% against experiences of diabetes patients.
+This result is significant because with the classifiers trained in this paper, it may be possible to not only detect multiple sclerosis from the patients’ clinical notes, but also from their social media posts.
+Resulting early diagnosis of MS allows immediate measures to be taken and the symptoms of MS to be controlled.
+\\
+\indent However, we concede that there are still some limitations in our work that can be improved by future research on this topic.
+Firstly, there can be further improvements in the construction of the control group of users.
+With control group two for example, we essentially work with only two diseases – MS and diabetes – which is not like diagnosis in a clinical context, where there are more diseases to account for.
+In future research therefore, we can have a control group with more illnesses, so the experiments more closely resemble a situation that primary healthcare providers face.
+In addition, newer, transformer models like BERT and GPT-2 can be applied to this task in future work.
+While constructing the dataset, although we remove any clause with the term “MS” to prevent the trivial text classification of post-diagnosis comments, we still assume that the experiences of a patient post-diagnosis are the same the same as the experiences of the patient pre-diagnosis.
+In future work, patients can be asked about their experiences before the diagnosis of MS to create a more reliable dataset for MS diagnosis.
 \bibliography{anthology,acl2020}
 \bibliographystyle{acl_natbib}
-
 \appendix
-
-\section{Appendices}
-\label{sec:appendix}
-
-\section{Supplemental Material}
-\label{sec:supplemental}
+% \section{Appendices}
+% \label{sec:appendix}
+% \section{Supplemental Material}
+% \label{sec:supplemental}
 

### 2022-09-12 paper.tex
added some figures

@@
 \usepackage{microtype}
+\usepackage{graphicx}
+\usepackage{subcaption}
 
@@
 \subsection{Dataset construction}
+\begin{figure}[h!]
+  \centering
+   \includegraphics[width=\linewidth]{usercommentdistribution.png}
+   \caption{User-Comment Distribution}
+  \label{fig:usercomment}
+\end{figure}
 \textbf{Diagnosed group.} To get textual comments outlining the experiences of MS patients, we will utilize free text data from the MSRegister database \citep{Ford:12}.
@@
 If every clause in a patient comment includes some MS-related term, then we omit the comment from our dataset.
-With this approach, we were able to get 6121 comments from ****** diagnosed users in our dataset.
+With this approach, we were able to get 6121 comments from 3037 diagnosed users in our dataset.
 \\
@@
 After identifying the users, we select random posts in their timeline to be included in our dataset.
-The number of posts we select per user is controlled such that the final user-comment distribution is kept the same as the diagnosed users in the dataset, as illustrated in Figure *******.
+The number of posts we select per user is controlled such that the final user-comment distribution is kept the same as the diagnosed users in the dataset, as illustrated in Figure \ref{fig:usercomment}.
 Finally, as a measure to prevent posts created by bots to be included in our dataset, no more than 5 duplicate posts were allowed by the same user.
@@
 Diabetes was chosen as the illness for the second control group because firstly, it is an incurable, chronic condition like MS, and secondly, it is relatively prevalent, so we can find enough users on social media to exactly match the number of MS-diagnosed users from the MSRegister dataset.
-The users were found by searching on Twitter and Reddit for high-precision diagnostic patterns (footnote), examples of which can be found in Figure *******.
+The users were found by searching on Twitter and Reddit for high-precision diagnostic patterns (footnote), examples of which can be found in Figure ****.
 After identifying these users, we only include posts where the user mentions their condition (that is, diabetes), because we would expect only those experiences to be presented to a primary healthcare provider.
@@
 \section{Datset Analysis}
+\begin{figure*}[h!]
+  \centering
+  \begin{subfigure}[b]{0.3\linewidth}
+    \includegraphics[width=\linewidth]{msregisterfinal.png}
+    \caption{Diagnosed Users (MS)}
+  \end{subfigure}
+  \hspace{1em}
+  \begin{subfigure}[b]{0.3\linewidth}
+    \includegraphics[width=\linewidth]{controlonefinal.png}
+    \caption{Control One (Generic)}
+  \end{subfigure}
+  \hspace{1em}
+  \begin{subfigure}[b]{0.3\linewidth}
+    \includegraphics[width=\linewidth]{controltwofinal.png}
+    \caption{Control Two (Diabetes)}
+  \end{subfigure}
+  \caption{Word Clouds For Different Parts Of The Dataset}
+  \label{fig:wordclouds}
+\end{figure*}
 To increase our understanding of the newly created dataset, we started by conducting some preliminary data analysis on our dataset. \\
-\indent To begin with, we created word clouds from the text given by the MS-diagnosed users (Figure ******a), the generic control one users (Figure ******b), and the diabetes control two users (Figure *****c).
+\indent To begin with, we created word clouds from the text given by the MS-diagnosed users (Figure \ref{fig:wordclouds}a), the generic control one users (Figure \ref{fig:wordclouds}b), and the diabetes control two users (Figure \ref{fig:wordclouds}c).
 Before creating each of these word clouds, the text was made lowercase, stop words were removed from the text, and the text was tokenized.
@@
 \indent In addition to generating the word clouds for the dataset, we decided to count the average number of tokens per comment for each part of the dataset.
-The results of this investigation are shown in Table **********.
+The results of this investigation are shown in Table ****.
 We observe that the average number of tokens is the greatest for the diabetes control group, lower for the MS-diagnosed control group and lowest for the generic social media control group.
@@
 The implications of this difference are further discussed in the next section.
+\begin{table}
+\centering
+\begin{tabular}{p{0.5\linewidth}p{0.4\linewidth}}
+\hline
+\textbf{Dataset} & \textbf{Average number of tokens per comment}\\
+\hline
+Diagnosed (MS) & {29.1} \\
+Control One (Generic) & {14.1} \\
+Control Two (Diabetes) & {85.3} \\ 
+\hline
+\end{tabular}
+\caption{Average number of tokens per comment for evry part of the dataset}
+\label{tab:}
+\end{table}
 \section{Experiments}

### 2022-09-13 paper.tex
Added results table

@@
 \usepackage{subcaption}
+\usepackage{array}
+\usepackage{multirow}
+\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
 
@@
 \section{Datset Analysis}
+\label{sec:dataanalysis}
 \begin{figure*}[h!]
@@
   \end{subfigure}
-  \caption{Word Clouds For Different Parts Of The Dataset}
+  \caption{Word Clouds For Each Part of the Dataset}
   \label{fig:wordclouds}
@@
 \indent In addition to generating the word clouds for the dataset, we decided to count the average number of tokens per comment for each part of the dataset.
-The results of this investigation are shown in Table ****.
+The results of this investigation are shown in \autoref{tab:avglengths}.
 We observe that the average number of tokens is the greatest for the diabetes control group, lower for the MS-diagnosed control group and lowest for the generic social media control group.
@@
 \end{tabular}
-\caption{Average number of tokens per comment for evry part of the dataset}
-\label{tab:}
+\caption{Average number of tokens per comment for every part of the dataset}
+\label{tab:avglengths}
 \end{table}
@@
 \\
-\indent \textbf{K-Nearest Neighbours (KNN).} For the KNN classifier, we set the value k to 1, 2, 3, 5, 8, 10, and 100. The best accuracy was then recorded in Table ***. \\
+\indent \textbf{K-Nearest Neighbours (KNN).} For the KNN classifier, we set the value k to 1, 2, 3, 5, 8, 10, and 100. The best accuracy was then recorded in \autoref{tab:results}. \\
 \indent \textbf{Neural Network.} We decided to investigate both a single-layer neural network and two-layer neural network.
@@
 For the two-layer neural network, we set the number of neurons in the hidden layer to 50, 100 and 200.
-After testing these hyperparameters, the best accuracy was then recorded in Table ****.
+After testing these hyperparameters, the best accuracy was then recorded in \autoref{tab:results}.
 \\
@@
 Furthermore, the RNN, by nature of being a sequential model, exemplifies the difference between input sequence lengths.
-Since we know that the average comment length varies considerably in different sections of the dataset, as shown in Table **** in Section ****, for RNNs we particularly need to make sure that the classifier does not rely only on the length of the text for classification.
+Since we know that the average comment length varies considerably in different sections of the dataset, as shown in Table \ref{tab:avglengths} of \autoref{sec:dataanalysis}, for RNNs we particularly need to make sure that the classifier does not rely only on the length of the text for classification.
 Therefore, we set the number of RNN units to minimum of the average comment lengths of the datasets in question (rounded up).
-Accordingly, from the values in Table **** in Section ****, we set the number of RNN units for diagnosed users vs.
+Accordingly, from the values in \autoref{tab:avglengths} of \autoref{sec:dataanalysis}, we set the number of RNN units for diagnosed users vs.
 control one (generic) to be 15 and diagnosed users vs.
@@
 \\
-\indent The results for each of these classification models are reported in Table ****. \\
-****Tables \\
+\indent The results for each of these classification models are reported in \autoref{tab:results}. \\
+\begin{table*}
+\centering
+\begin{tabular}{p{0.12\linewidth}p{0.1\linewidth}p{0.05\linewidth}p{0.1\linewidth}p{0.12\linewidth}p{0.05\linewidth}p{0.1\linewidth}p{0.1\linewidth}}
+\hline\hline
+ & & \multicolumn{3}{C{0.25\linewidth}}{\textbf{MS-Diagnosed vs. Control One (Generic)}} & \multicolumn{3}{C{0.25\linewidth}}{\textbf{MS-Diagnosed vs. Control Two (Diabetes)}}\\
+ & & BoW & tfidf-BoW & Embeddings &  BoW & tfidf-BoW & Embeddings\\
+\hline
+\multirow{3}{\linewidth}{\textbf{Logistic Regression}} & Precision & 96.3 & 95.2	& 90.5 & 90.3 & 90.2 & 87.4\\
+ & Accuracy & 92.9 & 93.3 & 91.8 & 91.3 & 91.7 & 86.4 \\
+ & Recall & 90.5 & 92.0 & 93.3 & 92.5 & 93.4 & 86.3 \\
+\hline
+\multirow{3}{\linewidth}{\textbf{Naïve Bayes}} & Precision & 88.6 & 89.2 & 85.4 & 93.4 & 93.8 & 86.8\\
+ & Accuracy & 91.0 & 91.6 & 87.5 & 92.0 & 92.4 & 77.2\\
+ & Recall & 93.6 & 94.2 & 89.7 & 91.2 & 91.6 & 73.5\\
+\hline
+\multirow{3}{\linewidth}{\textbf{KNN}} & Precision & 70.8	& 66.6 & 85.0 & 71.5 & 83.0 & 94.6\\
+ & Accuracy & 83.5 & 78.3 & 87.1 & 77.3 & 85.1 & 77.8\\
+ & Recall & 96.1 & 88.1 & 89.2 & 81.3 & 87.2 & 71.4\\
+\hline
+\multirow{3}{\linewidth}{\textbf{1-Layer Neural Network}} & Precision & 94.2 & 92.4 & 94.8 & 92.3 & 90.9 & 91.5\\
+ & Accuracy & 92.3 & 92.6 & 93.9 & 91.5 & 90.8 & 89.8\\
+ & Recall & 91.2 & 93.2 & 93.4 & 91.1 & 91.2 & 88.9\\
+\hline
+\multirow{3}{\linewidth}{\textbf{2-Layer Neural Network}} & Precision & 94.1 & 95.0 & 95.8 & 90.2 & 90.6 & 88.7\\
+ & Accuracy & 92.9 & 93.3 & 94.3 & 90.8 & 91.6 & 90.1\\
+ & Recall & 92.3 & 92.2 & 93.2 & 91.7 & 92.9 & 91.7\\
+\hline
+\multirow{3}{\linewidth}{\textbf{RNN}} & Precision & N/A & N/A & 80.2 & N/A & N/A & 84.9\\
+ & Accuracy & N/A & N/A & 86.7 & N/A & N/A & 88.7\\
+ & Recall & N/A & N/A & 92.8 & N/A & N/A & 92.4\\
+\hline
+\multirow{3}{\linewidth}{\textbf{LSTM}} & Precision & N/A & N/A & 94.1 & N/A & N/A & 88.7\\
+ & Accuracy & N/A & N/A & 94.1 & N/A & N/A & 90.8\\
+ & Recall & N/A & N/A & 94.4 & N/A & N/A & 92.2\\
+\hline\hline
+\end{tabular}
+\caption{Results for all the classification models}
+\label{tab:results}
+\end{table*}
 \indent Overall, for control one, word embeddings with a two-layer neural network obtained the best accuracy of 94.3\%.

### 2022-09-13 paper.tex
Fixed some formatting issues

@@
 \indent Our work has the following important improvements over existing literature.
-To create our dataset, we utilize a unique approach where we combine data from social media with the data from the MSRegister database, a database of clinically diagnosed MS patients from the UK \citep{Ford:12}.
-Since the MSRegister database has a relatively large number of MS patients, with this approach we were able to create the largest ever dataset for computerized MS diagnosis from free text.
+To create our dataset, we utilize a unique approach where we combine data from social media with the data from the MS Register database, a database of clinically diagnosed MS patients from the UK \citep{Ford:12}.
+Since the MS Register database has a relatively large number of MS patients, with this approach we were able to create the largest ever dataset for computerized MS diagnosis from free text.
 Moreover, existing research in free text MS diagnosis is also limited because most research relies on only one type of predictive classifier.
@@
 \\
-\indent Our contributions are as follows: \emph{(i)} create the largest ever dataset for computerized MS diagnosis from free text by combining the data from the existing MSRegister dataset with newly collected social media data \emph{(ii)} perform data analysis on this newly created dataset \emph{(iii)} build and train binary classifiers on the dataset to detect multiple sclerosis from patient free text.
+\indent Our contributions are as follows: \emph{(i)} create the largest ever dataset for computerized MS diagnosis from free text by combining the data from the existing MS Register dataset with newly collected social media data \emph{(ii)} perform data analysis on this newly created dataset \emph{(iii)} build and train binary classifiers on the dataset to detect multiple sclerosis from patient free text.
 \section{Related work}
@@
 To build binary classifiers for detecting multiple sclerosis from free text, we need a dataset containing experiences of both people with and people without MS, in text format.
-In this section, we describe how such a dataset was constructed by combining the data from social media platforms with data from the MSRegister database \citep{Ford:12}.
+In this section, we describe how such a dataset was constructed by combining the data from social media platforms with data from the MS Register database \citep{Ford:12}.
 We then discuss the privacy and ethical issues surrounding the construction of our dataset.
@@
 \end{figure}
-\textbf{Diagnosed group.} To get textual comments outlining the experiences of MS patients, we will utilize free text data from the MSRegister database \citep{Ford:12}.
+\textbf{Diagnosed group.} To get textual comments outlining the experiences of MS patients, we will utilize free text data from the MS Register database \citep{Ford:12}.
 We chose to use this database because it provides a large, rich resource of experiences of patients diagnosed with MS, in text format.
@@
 \\
-\indent \textbf{Control group.} To get the experiences of users who do not have MS (that is, the control group), we chose social media platforms because, like the MSRegister database, people share their experiences in text format on these platforms.
+\indent \textbf{Control group.} To get the experiences of users who do not have MS (that is, the control group), we chose social media platforms because, like the MS Register database, people share their experiences in text format on these platforms.
 Twitter and Reddit were chosen as the social media platforms because they are popular platforms where users often post in plain text about their general life experiences.
@@
 \indent Therefore, the second control group are comments of users who have given self-reported diagnoses of diabetes on social media (both type 1 and type 2), and who, like the first control group, have not mentioned “MS” or any related terms in their timeline.
-Diabetes was chosen as the illness for the second control group because firstly, it is an incurable, chronic condition like MS, and secondly, it is relatively prevalent, so we can find enough users on social media to exactly match the number of MS-diagnosed users from the MSRegister dataset.
-The users were found by searching on Twitter and Reddit for high-precision diagnostic patterns (footnote), examples of which can be found in Figure ****.
+Diabetes was chosen as the illness for the second control group because firstly, it is an incurable, chronic condition like MS, and secondly, it is relatively prevalent, so we can find enough users on social media to exactly match the number of MS-diagnosed users from the MS Register dataset.
+The users were found by searching on Twitter and Reddit for high-precision diagnostic patterns (footnote).
 After identifying these users, we only include posts where the user mentions their condition (that is, diabetes), because we would expect only those experiences to be presented to a primary healthcare provider.
@@
 We replaced social media usernames with user identifier codes to anonymise their identity.
-Although the MSRegister database contains identifiable information, including the gender and date of birth of the patients, this database was accessed through a secure virtual desktop environment, so the identifiable information remains private.
-For both the patients in the MSRegister database and the social media users, we made no attempt identify the users with other external sources of information.
+Although the MS Register database contains identifiable information, including the gender and date of birth of the patients, this database was accessed through a secure virtual desktop environment, so the identifiable information remains private.
+For both the patients in the MS Register database and the social media users, we made no attempt identify the users with other external sources of information.
 Therefore, this research was conducted in compliance to the GDBR guidelines of data protection \citep{GDBR:16}.
@@
   \end{subfigure}
-  \hspace{1em}
+  \hspace{0.5em}
   \begin{subfigure}[b]{0.3\linewidth}
@@
 \end{figure*}
+\begin{table*}
+\centering
+\begin{tabular}{lcc}
+\hline
+\textbf{Dataset} & \textbf{\hspace{1.5cm}Average comment length (in number of tokens)\hspace{1.1cm}} & \hspace{1cm}\\
+\hline
+Diagnosed (MS) & 29.1 & \\
+Control One (Generic) & 14.1 & \\
+Control Two (Diabetes) & 85.3  & \\ 
+\hline
+\end{tabular}
+\caption{Average number of tokens per comment for every part of the dataset}
+\label{tab:avglengths}
+\end{table*}
 To increase our understanding of the newly created dataset, we started by conducting some preliminary data analysis on our dataset. \\
@@
 The implications of this difference are further discussed in the next section.
-\begin{table}
-\centering
-\begin{tabular}{p{0.5\linewidth}p{0.4\linewidth}}
-\hline
-\textbf{Dataset} & \textbf{Average number of tokens per comment}\\
-\hline
-Diagnosed (MS) & {29.1} \\
-Control One (Generic) & {14.1} \\
-Control Two (Diabetes) & {85.3} \\ 
-\hline
-\end{tabular}
-\caption{Average number of tokens per comment for every part of the dataset}
-\label{tab:avglengths}
-\end{table}
 \section{Experiments}
@@
 \\
-\indent \textbf{K-Nearest Neighbours (KNN).} For the KNN classifier, we set the value k to 1, 2, 3, 5, 8, 10, and 100. The best accuracy was then recorded in \autoref{tab:results}. \\
+\indent \textbf{K-Nearest Neighbours (KNN).} For the KNN classifier, we set the hyperparameter $k$ to 1, 2, 3, 5, 8, 10, and 100. The best accuracy was then recorded in \autoref{tab:results}. \\
 \indent \textbf{Neural Network.} We decided to investigate both a single-layer neural network and two-layer neural network.
@@
 \indent The results for each of these classification models are reported in \autoref{tab:results}. \\
-\begin{table*}
+\begin{table*}[!ht]
 \centering
@@
 \section{Conclusion}
-By employing a novel approach combining social media data with the MSRegister dataset of MS patients in the UK, we were able to create the largest ever dataset for computerized diagnosis for MS.
+By employing a novel approach combining social media data with the MS Register dataset of MS patients in the UK, we were able to create the largest ever dataset for computerized diagnosis for MS.
 We trained multiple different models on this dataset, and we were able to achieve a maximum accuracy of 94.3\% when classifying experiences of MS patients against generic social media text data and a maximum accuracy of 92.4\% against experiences of diabetes patients.

### 2022-09-14 paper.tex
Added footnotes

@@
 \usepackage{multirow}
+\usepackage[compact]{titlesec}
 \newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}
+\interfootnotelinepenalty=10000
 
@@
 \begin{abstract}
+Multiple Sclerosis (MS) is an important and growing concern for public health.
+Therefore, there is a need for inexpensive yet effective methods for diagnosis of MS.
+One such diagnosis method involves NLP-based predictive classifiers, which take as input patient experiences in text format.
+However, in order to employ NLP for MS diagnosis, we require a large-scale, high-quality, labelled dataset containing experiences of MS patients and individuals who do not have MS.
+In this paper, we introduce the largest ever dataset for MS diagnosis from patient free text data, created by combining social media text data with free text data from the MS Register database, a database of clinically diagnosed MS patients in the UK.
+We examine differences in language between the MS-diagnosed group and the control group, and we explore text classification methods to identify individuals with MS.
 \end{abstract}
@@
 However, since the classifier will be used pre-diagnosis, we cannot make this classifier rely on the term “multiple sclerosis”, or any other term that only MS patients will know about.
-Therefore, we remove all clauses containing MS-related terms (footnote with list link) from patient comments.
+Therefore, we remove all clauses containing MS-related terms\footnote{\url{https://www.doc.ic.ac.uk/~dj321/msnlp/msterms.txt}} from patient comments.
 If every clause in a patient comment includes some MS-related term, then we omit the comment from our dataset.
@@
 Moreover, we ignored image-only posts, video-only posts, Twitter retweets and Reddit cross-posts.
-For Reddit, we added the additional restriction that the potential control group user has never posted on any MS-related subreddit (footnote).
+For Reddit, we added the additional restriction that the potential control group user has never posted on any MS-related subreddit \footnote{\url{https://www.doc.ic.ac.uk/~dj321/msnlp/mssubreddits.txt}}.
 After identifying the users, we select random posts in their timeline to be included in our dataset.
@@
 Diabetes was chosen as the illness for the second control group because firstly, it is an incurable, chronic condition like MS, and secondly, it is relatively prevalent, so we can find enough users on social media to exactly match the number of MS-diagnosed users from the MS Register dataset.
-The users were found by searching on Twitter and Reddit for high-precision diagnostic patterns (footnote).
+The users were found by searching on Twitter and Reddit for high-precision diagnostic patterns \footnote{List of diagnosis patterns (\url{https://www.doc.ic.ac.uk/~dj321/msnlp/diagnosispatterns.txt}) was inspired by the work of \citet{Cohan:18} on NLP-based diagnosis of mental health disorders}.
 After identifying these users, we only include posts where the user mentions their condition (that is, diabetes), because we would expect only those experiences to be presented to a primary healthcare provider.
@@
 To handle hashtags, tags, and subreddit names in the text collected from social media, we removed the characters ‘\#’, ‘@’ and ‘r/’ from the start of every word in the free text, if the word started with any of those characters.
-Finally, we tokenized, lemmatized and removed stop words (footnote) from the text in the database.
+Finally, we tokenized, lemmatized and removed stop words\footnote{List of stop words (\url{https://www.doc.ic.ac.uk/~dj321/msnlp/stopwords.txt}) was inspired by NLTK's list of English stop words} from the text in the database.
 \\

### 2022-09-14 paper.tex
Added examples of diagnosis patterns

@@
 Moreover, we ignored image-only posts, video-only posts, Twitter retweets and Reddit cross-posts.
-For Reddit, we added the additional restriction that the potential control group user has never posted on any MS-related subreddit \footnote{\url{https://www.doc.ic.ac.uk/~dj321/msnlp/mssubreddits.txt}}.
+For Reddit, we added the additional restriction that the potential control group user has never posted on any MS-related subreddit\footnote{\url{https://www.doc.ic.ac.uk/~dj321/msnlp/mssubreddits.txt}}.
 After identifying the users, we select random posts in their timeline to be included in our dataset.
@@
 Diabetes was chosen as the illness for the second control group because firstly, it is an incurable, chronic condition like MS, and secondly, it is relatively prevalent, so we can find enough users on social media to exactly match the number of MS-diagnosed users from the MS Register dataset.
-The users were found by searching on Twitter and Reddit for high-precision diagnostic patterns \footnote{List of diagnosis patterns (\url{https://www.doc.ic.ac.uk/~dj321/msnlp/diagnosispatterns.txt}) was inspired by the work of \citet{Cohan:18} on NLP-based diagnosis of mental health disorders}.
+The users were found by searching on Twitter and Reddit for high-precision diagnostic patterns\footnote{List of diagnosis patterns (\url{https://www.doc.ic.ac.uk/~dj321/msnlp/diagnosispatterns.txt}) was inspired by the work of \citet{Cohan:18} on NLP-based diagnosis of mental health disorders}.
+Some examples of these patterns include \emph{``i have been diagosed with diabetes"}, \emph{``he diagnosed me with diabetes"} and \emph{``i have a diagnosis of diabetes"}.
 After identifying these users, we only include posts where the user mentions their condition (that is, diabetes), because we would expect only those experiences to be presented to a primary healthcare provider.
